Recent advances of Malaria parasites detection systems based on mathematical morphology techniques

### 2017-11-22 Paper.tex
Added new images and renewed fig.1. References ok. Conclusion reviewed.

	Peripheral blood smears analysis is a common and economical diagnosis technique by which expert pathologists may obtain health information about the patients. Although this procedure requires highly trained experts, it is error-prone and could be affected by inter-observer variations. Moreover, blood cells images taken from microscope could vary in their illumination and colouration conditions. Typical blood cells images contain three main components of interest: the platelets (or thrombocytes), the red blood cells (or erythrocytes) and the white blood cells (or leukocytes). It is worth considering that blood cells exist with different shapes, characteristics and colourations, according to their types.

@@

	\begin{figure}[!t]
		\centering
		\includegraphics[width=2.75cm]{img/f3_Pfalciparum}
		\includegraphics[width=2.75cm]{img/f3_Pvivax}
		\includegraphics[width=2.75cm]{img/f3_Povale}
		\includegraphics[width=2.75cm]{img/f3_Pmalariae}
		\caption{\label{fig:malaria_types}Types of human malaria: from left to right, P. Falciparum, P. Vivax, P. Ovale, P. Malariae \cite{Khan2011}.}
	\end{figure}

	\begin{figure}[!t]
		\centering
		\includegraphics[width=2.75cm, height=2.75cm]{img/1_Pfalciparum_ring}
		\includegraphics[width=2.75cm, height=2.75cm]{img/2_Pfalciparum_trophozoite}
		\includegraphics[width=2.75cm, height=2.75cm]{img/3_Pfalciparum_gametocyte}
		\includegraphics[width=2.75cm, height=2.75cm]{img/4_Pfalciparum_schizont}
		\includegraphics[width=2.75cm, height=2.75cm]{img/5_Pmalariae_ring}
		\includegraphics[width=2.75cm, height=2.75cm]{img/6_Pmalariae_schizont}
		\includegraphics[width=2.75cm, height=2.75cm]{img/7_Povale_trophozoites}
		\includegraphics[width=2.75cm, height=2.75cm]{img/8_Pvivax_trophozoites}
		\includegraphics[width=2.75cm, height=2.75cm]{img/9_Pvivax_ring}
		\includegraphics[width=2.75cm, height=2.75cm]{img/10_Pvivax_gametocyte}
		\includegraphics[width=2.75cm, height=2.75cm]{img/11_Pvivax_ring}
		\caption{\label{fig:malaria_stages}Examples of malaria parasite stages. From top left: P.falciparum ring, trophozoite, gametocyte, schizont; P.malariae ring and schizont; P.ovale and P.vivax trophozoites; P.vivax ring and gametocyte; P.vivax ring \cite{Tek2010}}
	\end{figure}

@@

	\begin{figure}[!t]
		\centering
		\includegraphics[height=0.15\textheight]{img/f2_ThickGiemsa}
		\includegraphics[height=0.15\textheight]{img/f2_ThickLeishman}
		\includegraphics[height=0.15\textheight]{img/f2_ThinGiemsa}
		\includegraphics[height=0.15\textheight]{img/f2_ThinLeishman}
		\caption{\label{fig:thick_thin_film}Malaria infected blood smear images. From top left, clockwise: thick smear with Giemsa stain, thick smear with Leishman stain, thin smear with Leishman stain, thick smear with Giemsa stain \cite{Das2015}. Arrows in top images indicate chromatin dots while, in the bottom ones, they show the infected erythrocytes.}
	\end{figure}

@@

	Another greatly used segmentation approach is clearly the watershed transform. The classic watershed approach is reported to produce over segmentation results \cite{Savkare2011}, whereas the marker controlled approach does not suffer from this issue and it is reported to be very effective for overlapping cells segmentation even though some authors affirm that it may fail to segment highly overlapped cells  (\cite{Das2011}, \cite{Das2013}, \cite{Das2014}, \cite{Das2015}, \cite{Devi2017}, \cite{Khan2011}, \cite{Romero2016}, \cite{Savkare2015}, \cite{Savkare2011a}, \cite{Springl2009}).

@@

	The computer vision methodologies reported in the literature are based on light microscopic images of human peripheral blood smears for computer-aided detection of malaria parasite and its various stages. Image preprocessing, segmentation of erythrocytes and parasites, malaria parasite feature extraction, malaria detection techniques have been discussed here.

@@

	Moreover, non-linear filtering has become increasingly important in many image processing applications. Initially, the attraction to non-linear filters was mostly limited to the impulse-removing and edge-preserving qualities of the median filter. However, as the number and sophistication of non-linear filters have increased, so has the variety of applications for these filters. The shape-based methods of mathematical morphology, in particular, are now used in a wide variety of medical applications, including electrocardiography, ultrasound imaging, radiology, and histologic image analysis \cite{Schulze1994}.

>>>>

Peripheral blood smears analysis is a common and economical diagnosis technique by which expert pathologists may obtain health information about the patients. Although this procedure requires highly trained experts, it is error-prone and could be affected by inter-observer variations. Moreover, blood cells images taken from microscope could vary in their illumination and colouration conditions, as shown in fig. \ref{fig:images_types}. Typical blood cells images contain three main components of interest: the platelets (or thrombocytes), the red blood cells (or erythrocytes) and the white blood cells (or leukocytes). It is worth considering that blood cells exist with different shapes, characteristics and colourations, according to their types.

@@

\begin{figure}[!t]
	\centering	
	\includegraphics[width=5cm]{img/f1a.eps}
	\includegraphics[width=5cm]{img/f1b.eps}
	\includegraphics[width=5cm]{img/f1c.eps}
	\includegraphics[width=5cm]{img/f1d.eps}
	\caption{\label{fig:images_types}Different illumination conditions generate different images, because of the absence of a standardized acquisition procedure. From left to right: acquisition of the same smear with four microscope's brightness levels.}
\end{figure}

\iftrue
\begin{figure}[!t]
	\centering
	\includegraphics[width=3.5cm]{img/f3_Pfalciparum}
	\includegraphics[width=3.5cm]{img/f3_Pvivax}
	\includegraphics[width=3.5cm]{img/f3_Povale}
%	\includegraphics[width=2.75cm]{img/f3_Pmalariae}
	\caption{\label{fig:malaria_types}Types of human malaria: from left to right, P. Falciparum in its schizont stage, P. Vivax in two gametocytes specimens and one ring stage, P. Ovale in its ring stage.}
\end{figure}
\fi

\iftrue
\begin{figure}[!t]
	\centering
	\includegraphics[width=2.75cm, height=2.75cm]{img/falciparum_1_ring}
	\includegraphics[width=2.75cm, height=2.75cm]{img/falciparum_2_trophozoiteAge}
	\includegraphics[width=2.75cm, height=2.75cm]{img/falciparum_3_schizont}
	\includegraphics[width=2.75cm, height=2.75cm]{img/falciparum_4_gametocyte}
	\includegraphics[width=2.75cm, height=2.75cm]{img/ovale_1_ring}
	\includegraphics[width=2.75cm, height=2.75cm]{img/ovale_2_trophozoite}
	\includegraphics[width=2.75cm, height=2.75cm]{img/ovale_3_schizont}
	\includegraphics[width=2.75cm, height=2.75cm]{img/ovale_4_gametocyte}
	\includegraphics[width=2.75cm, height=2.75cm]{img/vivax_1_ring}
	\includegraphics[width=2.75cm, height=2.75cm]{img/vivax_2c_trophozoiteDeveloped}
	\includegraphics[width=2.75cm, height=2.75cm]{img/vivax_4_gametocyte}
	\caption{\label{fig:malaria_stages}Examples of malaria parasite stages. From top left: P.falciparum ring, trophozoite, schizont, gametocyte;
		 P.ovale ring, trophozoite, schizont, gametocyte; P.vivax ring, developed trophozoite, gametocyte. \cite{Tek2010}}
\end{figure}
\fi

@@

\begin{figure}[!t]
	\centering
	\includegraphics[height=0.15\textheight]{img/f3_ThickGiemsa}
	\includegraphics[height=0.15\textheight]{img/f3_ThickLeishman}
	\includegraphics[height=0.15\textheight]{img/f3_ThinGiemsa}
	\includegraphics[height=0.15\textheight]{img/f3_ThinLeishman}
	\caption{\label{fig:thick_thin_film}Malaria infected blood smear images. From top left, clockwise: thick smear with Giemsa stain, thick smear with Leishman stain, thin smear with Leishman stain, thick smear with Giemsa stain \cite{Das2015}. Arrows in top images indicate chromatin dots while, in the bottom ones, they show the infected erythrocytes.}
\end{figure}

@@

Another greatly used segmentation approach is clearly the watershed transform. The classic watershed approach is reported to produce over segmentation results \cite{Savkare2011b}, whereas the marker controlled approach does not suffer from this issue and it is reported to be very effective for overlapping cells segmentation even though some authors affirm that it may fail to segment highly overlapped cells  (\cite{Das2011}, \cite{Das2013}, \cite{Das2014}, \cite{Das2015}, \cite{Devi2017}, \cite{Khan2011}, \cite{Romero2016}, \cite{Savkare2015}, \cite{Savkare2011a}, \cite{Springl2009}).

@@

The computer vision methodologies reported in the literature are based on light microscopic images of human peripheral blood smears for computer-aided detection of malaria parasites and their several stages. 
Image preprocessing, segmentation of erythrocytes and parasites, malaria parasite feature extraction, malaria detection techniques have been discussed here.

@@

Moreover, non-linear filtering has become increasingly important in many image processing applications. Initially, the attraction to non-linear filters was mostly limited to the impulse-removing and edge-preserving qualities of the median filter. However, as the number and sophistication of non-linear filters have increased, so has the variety of applications for these filters. The shape-based methods of mathematical morphology, in particular, are now used in a wide variety of medical applications, including electrocardiography, ultrasound imaging, radiology, and histological image analysis \cite{Schulze1994}.

### 2017-11-22 Table_sum.tex
Images to insert
Added new images and renewed fig.1. References ok. Conclusion reviewed.

    Anggraini \emph{et al.}, 2011 &
		- &
		thresholding + hole filling &	
		- &
		two (\emph{P.falciparum} infected and noninfected) + two life-cycle-stages &
		-
        \vspace{0.6cm}
		\\
    Arco \emph{et al.}, 2014 &
		- &
		adaptive thresholding + hole filling, closing, regional minima &	
		- &
		two (infected and noninfected) &
		-
		\vspace{0.6cm}
        \\
    Das \emph{et al.}, 2011 &
		- &
		marker controlled watershed &	
		opening, closing  &
		two (infected and noninfected) &
		-
		\vspace{0.6cm}
        \\

    Das \emph{et al.}, 2013 &
		- &
		marker controlled watershed &	
		- &
		three (\emph{P.falciparum}, \emph{P.vivax} infected and noninfected) + three life-cycle-stages per species &
		-
		\vspace{0.6cm}
        \\

    Das \emph{et al.}, 2014 &
		- &
		marker controlled watershed &	
		- &
		three (\emph{P.falciparum}, \emph{P.vivax} infected and noninfected) + three life-cycle-stages per species &
		-
		\vspace{0.6cm}
        \\

    Dave \emph{et al.}, 2017 &
		- &
		adaptive thresholding + erosion, dilation &	
		- &
		two (infected and noninfected) &
		-
		\vspace{0.6cm}
        \\

    Devi \emph{et al.}, 2017 &
		- &
		marker controlled watershed &	
		- &
		- &
		-
		\vspace{0.6cm}
        \\

        Dey \emph{et al.}, 2015 &
		- &
		opening &	
		- &
		- &
		-
		\vspace{0.6cm}
        \\

    Diaz \emph{et al.}, 2009 &
		- &
		inclusion tree &	
		- &
		two (\emph{P.falciparum} infected and noninfected) + three life-cycle-stages &
		-
\vspace{0.6cm}
		\\

    Di Ruberto \emph{et al.}, 2002 &
		- &
		thresholding + granulometry, watershed  transform &	
		skeleton &
		two (\emph{P.falciparum} infected and noninfected) + three life-cycle-stages &
		-
\vspace{0.6cm}
		\\

    Elter \emph{et al.}, 2011 &
		- &
		thresholding + black top-hat &	
		- &
		two (infected and noninfected) &
		-
		\vspace{0.6cm} \\

    Gonzalez-Betancourt \emph{et al.}, 2016  &
    	morphological filter, erosion-reconstruction, dilation-reconstruction, closing &
    	-  &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Ghosh \emph{et al.}, 2011  &
    	- &
    	thresholding + opening, closing  &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Kareem \emph{et al.}, 2012  &
    	dilation, erosion &
    	-  &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Khan \emph{et al.}, 2011  &
    	- &
    	marker controlled watershed  &
    	- &
    	five (\emph{P.falciparum}, \emph{P.vivax}, \emph{P.ovale}, \emph{P.malariae} infected, and noninfected) &
    	- \vspace{0.6cm} \\

    Khan \emph{et al.}, 2014  &
    	- &
    	- &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Malihi \emph{et al.}, 2013  &
    	- &
    	-  &
    	area granulometry &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Mushabe \emph{et al.}, 2013  &
    	- &
    	thresholding + quali op.  &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Oliveira \emph{et al.}, 2017  &
    	erosion &
    	-  &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

@@

    Rosado \emph{et al.}, 2017  &
    	- &
    	adaptive thresholding + closing  &
    	- &
    	- &
    	- \vspace{0.6cm} \\

    Ross \emph{et al.}, 2006  &
    	area closing &
    	thresholding + granulometry, opening, reconstruction, morphological gradient, closing, thinning  &
    	erosion, dilation &
    	- &
    	- \vspace{0.6cm} \\

    Sheikhhosseini \emph{et al.}, 2013  &
    	hole filling, opening &
    	-  &
    	- &
    	- &
    	- \vspace{0.6cm} \\

    Savkare \emph{et al.}, 2011a  &
    	- &
    	watershed transform  &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Savkare \emph{et al.}, 2011b  &
    	- &
    	thresholding + hole filling, watershed transform  &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Savkare \emph{et al.}, 2015  &
    	- &
    	thresholding + watershed transform, erosion, dilation  &
    	- &
    	- &
    	- \vspace{0.6cm} \\

    {\v{S}}pringl, 2009  &
    	- &
    	thresholding + marker controlled watershed transform  &
    	area granulometry &
    	- &
    	- \vspace{0.6cm} \\

Somasekar \emph{et al.}, 2011  &
    	- &
    	- &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Somasekar \emph{et al.}, 2015  &
    	erosion, hole filling &
    	-  &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Somasekar \emph{et al.}, 2017  &
    	- &
    	thresholding + erosion, closing  &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Soni \emph{et al.}, 2011  &
    	- &
    	thresholding + granulometry, morphological gradient, dilation  &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Sulistyawati \emph{et al.}, 2015  &
    	- &
    	blob analysis + erosion, dilation, opening, closing  &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

 Tek \emph{et al.}, 2006  &
    	- &
    	top-hat, infinite reconstruction  &
    	area granulometry &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Tek \emph{et al.}, 2010  &
    	closing, granulometry &
    	thresholding + granulometry, area top-hat, closing  &
    	area granulometry &
    	five (\emph{P.falciparum}, \emph{P.vivax}, \emph{P.ovale}, \emph{P.malariae} infected, and noninfected) + 
    four life-cycle-stages for species &
    	- \vspace{0.6cm} \\

    Yunda \emph{et al.}, 2012  &
    	- &
    	thresholding + morphological gradient, erosion, dilation  &
    	- &
    	- &
    	- \\

@@

	\caption{Summary of analysed methods: morphological operations used in the main phases of analysis, kind of classification and performance measures.} % needs to go inside longtable environment
	\label{tab:summary_table}
	\end{longtable}

>>>>

    Anggraini \emph{et al.}, 2011 &
		- &
		thresholding + hole filling &	
		- &
		two (\emph{P.falciparum} infected and noninfected) + two life-cycle-stages &
		SE=93\% SP=99\%
        \vspace{0.6cm}
		\\
    Arco \emph{et al.}, 2014 &
		- &
		adaptive thresholding + hole filling, closing, regional minima &	
		- &
		two (infected and noninfected) &
		Acc=96.46\%
		\vspace{0.6cm}
        \\
    Das \emph{et al.}, 2011 &
		- &
		marker controlled watershed &	
		opening, closing  &
		two (infected and noninfected) &
		Acc=88.77\%
		\vspace{0.6cm}
        \\

    Das \emph{et al.}, 2013 &
		- &
		marker controlled watershed &	
		- &
	three (\emph{P.falciparum}, \emph{P.vivax} infected and noninfected) + three life-cycle-stages per species &
		Acc=84\%
		\vspace{0.6cm}
        \\

    Das \emph{et al.}, 2014 &
		- &
		marker controlled watershed &	
		- &
	three (\emph{P.falciparum}, \emph{P.vivax} infected and noninfected) + three life-cycle-stages per species &
		SE=99.72\% SP=84.39\%
		\vspace{0.6cm}
        \\

    Dave \emph{et al.}, 2017 &
		- &
		adaptive thresholding + erosion, dilation &	
		- &
		two (infected and noninfected) &
		Acc=97.83\% thin films, Acc=89.88\% thick films
		\vspace{0.6cm}
        \\

    Devi \emph{et al.}, 2017 &
		- &
		marker controlled watershed &	
		- &
		two (infected and noninfected)  &
		Acc=98.02\%
		\vspace{0.6cm}
        \\

    Diaz \emph{et al.}, 2009 &
		- &
		inclusion tree &	
		- &
		two (\emph{P.falciparum} infected and noninfected) + three life-cycle-stages &
		SE=94\% SP=99.7\% for detection, SE=78.8\% SP=91.2\% for life-stages
\vspace{0.6cm}
		\\

    Di Ruberto \emph{et al.}, 2002 &
		area closing &
		thresholding + granulometry, watershed  transform &	
		skeleton &
		two (\emph{P.falciparum} infected and noninfected) + three life-cycle-stages &
		-
\vspace{0.6cm}
		\\

    Elter \emph{et al.}, 2011 &
		- &
		thresholding + black top-hat, dilation &	
		- &
		two (infected and noninfected) &
		SE=97\%
		\vspace{0.6cm} \\

    Gonzalez-Betancourt \emph{et al.}, 2016  &
    	morphological filter, erosion-reconstruction, dilation-reconstruction, closing &
    	-  &
    	- &
    	- &
    	- \vspace{0.6cm} \\

    Ghosh \emph{et al.}, 2011  &
    	- &
    	thresholding + opening, closing  &
    	- &
    	two (\emph{P.vivax} infected and noninfected) &
    	- \vspace{0.6cm} \\

    Kareem \emph{et al.}, 2012  &
    	dilation, erosion &
    	-  &
    	- &
    	two (infected and noninfected) &
    	Acc=88\% SE=90\% SP=86\% \vspace{0.6cm} \\

    Khan \emph{et al.}, 2011  &
    	area closing &
    	thresholding + granulometry, opening, morphological reconstruction, gradient, dilation &
    	- &
    	five (\emph{P.falciparum}, \emph{P.vivax}, \emph{P.ovale}, \emph{P.malariae} infected, and noninfected) &
    	Acc=81\% SE=85.5\% \vspace{0.6cm} \\

    Khan \emph{et al.}, 2014  &
    	- &
    	- &
    	- &
    	two (infected and noninfected) &
    	SE=93\% SP=95\% \vspace{0.6cm} \\

    Malihi \emph{et al.}, 2013  &
    	closing &
    	-  &
    	area granulometry &
    	two (infected and noninfected) &
    	Acc=91\% SE=80\% SP=95.5\% \vspace{0.6cm} \\

    Mushabe \emph{et al.}, 2013  &
    	closing &
    	thresholding + granulometry, dilation, erosion  &
    	- &
    	two (infected and noninfected) &
    	SE=98.5 SP=97.2\% \vspace{0.6cm} \\

    Oliveira \emph{et al.}, 2017  &
    	erosion &
    	-  &
    	- &
    	two (infected and noninfected) &
    	Acc=91\% \vspace{0.6cm} \\

@@

    Rosado \emph{et al.}, 2017  &
    	- &
    	adaptive thresholding + closing  &
    	- &
    	four (\emph{P.falciparum}, \emph{P.ovale}, \emph{P.malariae} infected, and noninfected) +
    three life-cycle-stages for species &
    	SE=73.9-96.2\% SP=92.6-99.3\% \vspace{0.6cm} \\

    Ross \emph{et al.}, 2006  &
    	area closing &
    	thresholding + granulometry, opening, reconstruction, morphological gradient, closing, thinning  &
        - &
    	five (\emph{P.falciparum}, \emph{P.vivax}, \emph{P.ovale}, \emph{P.malariae} infected, and noninfected) &
    	SE=85\% for detection, Acc=73\% for classification
    	 \vspace{0.6cm} \\

    Savkare \emph{et al.}, 2011a  &
    	- &
    	thresholding + hole filling, watershed transform  &
    	- &
    	two (infected and noninfected) &
    	- \vspace{0.6cm} \\

    Savkare \emph{et al.}, 2011b  &
    	- &
    	thresholding + hole filling, watershed transform  &
    	- &
    	two (infected and noninfected) &
    	SE=93.12\% SP=93.17\% \vspace{0.6cm} \\

    Savkare \emph{et al.}, 2015  &
    	- &
    	thresholding + watershed transform, erosion, dilation  &
    	- &
    	two (infected and noninfected) &
    	Acc=95.5\% \vspace{0.6cm} \\

    Sheikhhosseini \emph{et al.}, 2013  &
    	- &
    	thresholding + hole filling, opening  &
    	- &
    	two (infected and noninfected) &
    	Acc=97.25\% SE=82.21\% SP=98.02\% \vspace{0.6cm} \\

    Somasekar \emph{et al.}, 2015  &
    	- &
    	fuzzy C-means clustering + erosion, hole filling  &
    	- &
    	two (infected and noninfected) &
    	SE=98\% SP=93.3\% \vspace{0.6cm} \\

    Somasekar \emph{et al.}, 2017  &
    	- &
    	thresholding + erosion, closing, hole filling  &
    	- &
    	two (infected and noninfected) &
    	average DSC=0.8 \vspace{0.6cm} \\

    Soni \emph{et al.}, 2011  &
    	- &
    	thresholding + granulometry, morphological gradient, dilation  &
    	- &
    	five (\emph{P.falciparum}, \emph{P.vivax}, \emph{P.ovale}, \emph{P.malariae} infected, and noninfected) &
    	SE=98\% for detection  \vspace{0.6cm} \\

{\v{S}}pringl, 2009  &
    	closing &
    	thresholding + marker controlled watershed transform, hole filling, dilation, opening, erosion  &
    	- &
    	two (infected and noninfected) &
    	AUC=0.98 \vspace{0.6cm} \\

    Sulistyawati \emph{et al.}, 2015  &
    	- &
    	blob analysis + erosion, dilation, opening, closing, hole filling  &
    	- &
    	two (infected and noninfected) &
    	Acc=99.39\% \vspace{0.6cm} \\

 Tek \emph{et al.}, 2006  &
    	- &
    	top-hat, infinite reconstruction  &
    	area granulometry &
    	two (infected and noninfected) &
    	SE=74\% SP=98\% \vspace{0.6cm} \\

    Tek \emph{et al.}, 2010  &
    	closing, granulometry &
    	thresholding + granulometry, area top-hat, closing  &
    	area granulometry &
    	five (\emph{P.falciparum}, \emph{P.vivax}, \emph{P.ovale}, \emph{P.malariae} infected, and noninfected) +
    four life-cycle-stages for species &
    	SE=72\% SP=98\% \vspace{0.6cm} \\

    Yunda \emph{et al.}, 2012  &
    	- &
    	thresholding + morphological gradient, erosion, dilation  &
    	- &
    	three (\emph{P.falciparum}, \emph{P.vivax} infected, and noninfected) + two life-cycle-stages for \emph{P.falciparum}&
    	SE=77.19\% \\

@@

	\caption{Summary of analysed methods: morphological operations used in the main phases of analysis, kind of classification and performance measures (Sensitivity, Specificity, Accuracy, if reported).} % needs to go inside longtable environment
	\label{tab:summary_table}
	\end{longtable}
